---
title: "ABDS User Maunal"
author: "Dongping Du"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We developed the ABDS tool suite specifically for analyzing biologically diverse samples. Mechanism-integrated group-wise pre-imputation is designed to recruit signature genes that represent informative missingness, a cosine-based one-sample test is extended to detect downregulated signature genes, and a unified heatmap is designed to display multiple phenotypic groups. We discuss the methodological principles and demonstrate the effectiveness of three analytics tools, supported by comparative evaluations and biomedical showcases.

## Quick Start
You can install the latest version of ABDS from GitHub by
```{r, eval = FALSE}
devtools::install_github("niccolodpdu/ABDS")
```

## MGpI: Mechanism-integrated group-wise pre-imputation


## eCOT: Extended Cosine-based One-sample Test


## uniHM: Unified heatmap design for comparative display

